DOM Review Summary

### 2024-03-15 Analysis/ReviewSummary/ReviewSummary.qmd
Taxa categories/counts
Added table for taxa category and plot for taxa counts

@@

@@

>>>>

```{r Species_clean}
species_clean <- review_SpeciesLocation |>
  filter(Status == "Complete") |>
  mutate(ID_clean = str_extract(ID, "[:digit:]+"))
```

@@

```{r Species_Taxa}
#| echo: false

species_taxaTable <-species_clean |>
  separate_rows(Taxa_Category, sep = ", ") |>
  mutate(Total = length(unique(ID_clean))) |>
  select(Taxa_Category, ID_clean, Total) |>
  distinct() |>
  summarise(Articles = n(), 
            Proportion = round(Articles/mean(Total), 2),
            .by = Taxa_Category) |>
  arrange(-Articles) |>
  rename(Taxa = Taxa_Category)
```

DOMs have been widely used for terrestrial taxa, with numerous examples modelling bird, mammal, and herptile occupancy dynamics. `{r} species_taxaTable$Articles[species_taxaTable$Taxa == "Threatened"]` articles described their focal species as threatened in some way; `{r} species_taxaTable$Articles[species_taxaTable$Taxa == "Invasive"]` fit models to invasive species.

```{r Species_TaxaTable}
#| echo: false

kable(species_taxaTable)
```

@@

```{r Species_Number}
#| echo: false
species_Number <- species_clean |>
  select(ID_clean, Taxa_Number) |>
  mutate(Taxa_Number = sum(Taxa_Number), .by = ID_clean)
```

Only approximately half of articles modelled occupancy dynamics for a single species. Others fit multiple occupancy models: either multi-species models where 2+ species were modelled in concert, or many independent models for a suite of species. The largest number of species modelled in a single paper was **`{r} max(species_Number$Taxa_Number)`**.

```{r Species_NumberPlot}
#| echo: false

species_Number |>
  mutate(NumberGroup = case_when(Taxa_Number == 1 ~ "1",
                                 Taxa_Number %in% 2:10 ~ "2-10",
                                 Taxa_Number %in% 11:100 ~ "11-100",
                                 Taxa_Number > 100 ~ ">100")) |>
  summarise(Articles = n(), .by = NumberGroup) |>
  mutate(NumberGroup = fct(NumberGroup,
                           levels = c("1", "2-10", "11-100", ">100"))) |>

  ggplot() +
  geom_col(aes(x = NumberGroup, y = Articles), fill = "darkslategrey") +
  labs(title = "Number of species modelled per article",
       x = "Number of species", y = "Number of articles") 
```
